### 2012-07-03 inst/examples/bias_table.Rmd
low is actually very high now
updated labels
updated

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bias_table/", verbose=TRUE or`

@@

With parameter `r` = `r r <- 0.5`

@@

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(low=opt_low, med=opt_med, high=opt_high)
par_list <- list(c(0.5, 100), c(1, 100), c(1.5, 100))

>>>>

`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="bias_table/", verbose=TRUE or`

@@

@@

With parameter `r` = `r r <- 2`

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(low=opt_low, med=opt_med, high=opt_high)
par_list <- list(c(1, 100), c(1.5, 100), c(2, 100))
